Mood increases during video game play: A naturalistic observational case study of PowerWash Simulator

### 2023-09-14 ms.qmd
use correct env var

dir.create("models", FALSE)
N_CORES <- as.numeric(Sys.getenv("N_CORES", unset = 1))
N_THREADS <- as.numeric(Sys.getenv("N_THREADS", unset = 2))
N_ITER <- as.numeric(Sys.getenv("N_THREADS", unset = 2000))
N_SUBSET <- as.numeric(Sys.getenv("N_SUBSET"))
options(
  mc.cores = N_CORES,
  brms.backend = "cmdstanr"
)
theme_set(
  theme_linedraw(base_size = 10) +
    theme(
      strip.background = element_rect(fill = NA, color = NA),
      strip.text = element_text(colour = "black", hjust = 0),
      axis.text = element_text(size = rel(0.75)),
      panel.grid = element_blank()
    )
)
```

>>>>

dir.create("models", FALSE)
N_CORES <- as.numeric(Sys.getenv("N_CORES", unset = 1))
N_THREADS <- as.numeric(Sys.getenv("N_THREADS", unset = 2))
N_ITER <- as.numeric(Sys.getenv("N_ITER", unset = 2000))
N_SUBSET <- as.numeric(Sys.getenv("N_SUBSET"))
options(
  mc.cores = N_CORES,
  brms.backend = "cmdstanr"
)
theme_set(
  theme_linedraw(base_size = 10) +
    theme(
      strip.background = element_rect(fill = NA, color = NA),
      strip.text = element_text(colour = "black", hjust = 0),
      axis.text = element_text(size = rel(0.75)),
      panel.grid = element_blank()
    )
)
```
